Dish: Distribution-oblivious Shell Scripting

### 2020-01-08 pldi/draft.tex
Teensy corrections to paper

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review,anonymous]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

@@

@@

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
\textbf{Distributability description language.}
The DSL captures important information regarding the distributability of a command.
\vspace{-20pt}
}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.70\columnwidth]{\detokenize{./figs/dish_g1.pdf}}
\caption{
  \textbf{Example graph transformation.}
  The optimizer splits a stateless node to utilize
  available data parallelism.
}
\vspace{-10pt}
\label{fig:optimizer-transformation}
\end{figure}

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[sigplan,10pt,review,anonymous]{acmart}
\settopmatter{printfolios=false,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[sigplan]{acmart}\settopmatter{}

@@

\kk{After discussion on Wednesday Jan 8: Modify the narrative of this paper to talk about data processing in the Shell. Make this the main focus of the paper. This simplifies the narrative and allows us to not talk about late planner activation as well as environment variables. It also justifies why we only deal with pure and stateless. Note that this is a very expressive model, as shown by our benchmark suite. Note: Rememeber to clearly describe the subset of the shell that we handle. To be more precise the compositional operator of the shell that we can handle.}

@@

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
\textbf{Distributability description language.}
The DSL captures important information regarding the distributability of a command.
\vspace{-10pt}
}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.40\columnwidth]{\detokenize{./figs/dish_g1.pdf}}
\caption{
  \textbf{Example graph transformation.}
  The optimizer splits a stateless node to utilize
  available data parallelism.
}
\vspace{-10pt}
\label{fig:optimizer-transformation}
\end{figure}
